
% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.5in}
\addtolength{\oddsidemargin}{-0.5in}

% the margin option causes section titles to appear to the left of body text 
\textwidth=5.9in % increase textwidth to get smaller right margin
%\usepackage[cmintegrals,cmbraces]{newtxmath}
%\%usepackage{ebgaramond-maths}
%\usepackage[T1]{fontenc}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage{utopia}
%
%\usepackage{literat}
%\usepackage[urw-garamond]{mathdesign}
%\usepackage[T1]{fontenc}
\usepackage{setspace}
\renewcommand{\baselinestretch}{0.5} 
%\renewcommand{\familydefault}{\sfdefault}
%\renewcommand*\rmdefault{ppl}
%\renewcommand*\rmdefault{iwona}

\begin{document} 

\name{Tigany Noor Abubaker Tigany Zarrouk\\ Email: tiganyzarrouk@gmail.com\\ Tel: +447833198259\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Present Address} \\ 119 Latymer Court \\ Hammersmith Road \\ London, W6 7JF}
\address{{\bf Permanent Address} \\ 174 Crompton Way \\ Bolton, BL2 2SA \\}

 
\begin{resume} 
 
%\section{Objective} 
%Auditing/Analysis of Operations 

\section{Education}
{\bf Imperial College London}\hfill September 2013--June 2017\\
MSci. Hons. Physics (Expected 2:1)---4\textsuperscript{th} Year Undergraduate\\
%Relevant courses
Computational Physics, Quantum Theory of Matter, Light and Matter, Solid State, Group Theory, Foundations of Quantum Mechanics, Quantum Field Theory, Quantum Information, Advanced Classical Mechanics, Nuclear and Particle Physics, Mathematical Methods.

{\bf Bolton School Boys' Division} \hfill 2006--2013 \\
A-levels: Physics (A*), Maths (A*), Further Maths (A*), Chemistry (A)\\
GCSE's: 6 A*s, 4 As
 

\section{Relevant\\ Experience}

%\singlespacing
 {\bf Undergraduate Research Opportunities Programme} \hfill July 2016--September 2016\\ Imperial College London
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item 9-week, full-time research placement.
 \item Developed homoepitaxial growth model of GaAs with deposition and diffusion events using a Kinetic Monte Carlo algorithm.
\item Extended model with the addition of another molecular species with differing properties. 
\item Analysed number of adatoms, island size and differences in crystal growth.
\end{itemize}


 {\bf MSci Project,} Imperial College London \hfill October 2016--Present
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item Developed cellular automaton model of non-linear, electrical wave dynamics in the heart which spontaneously give rise to Atrial Fibrillation.
\item Extended model to work on more realistic heart morphology to investigate new phenomena. 
\end{itemize}



 {\bf Computational Projects,} Imperial College London \hfill October 2013--December 2015
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item Modelled silver spheres in resin to find the Critical threshold for conductivity.
\item Optimised the design of a pion accelerator and detector to measure branching ratios.
 \item Investigated the properties and dynamics of solitons under the Kortweg De-Vries Equation.
\item Simulated double pendula and investigated dynamics under varous finite difference methods.



 \end{itemize}

 {\bf Head of Research and Design,}\hfill October 2011--April 2012\\ EDT Engineering Education Scheme---Lancaster University \& United Utilities 
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Designed and created Silt Trap with a team of 5.
\item Researched advanced concepts in Fluids and applied them.
\item Used university facilities---flow tanks and meters to test and improve design.
\item Member of multidisciplinary team to produce results within deadlines.
 \item Wrote report and presented solution to panel of Senior Engineers.
 
 \end{itemize}


 \section{Additional Experience} 
{\bf Work Shadowing of Technician,} Quay Pharmaceuticals \hfill  Summer 2011
\begin{itemize} \itemsep -2pt %reduce space between items
\item Practical experience with laboratory equipment: High Performance Liquid Chromatography Machine.
\item Measured specific properties of substances for analysis.
\item Absorbed information quickly and efficiently to work within deadline.
\end{itemize}

{\bf Business Enterprise and Training Course} \hfill Summer 2011
\begin{itemize} \itemsep -2pt
\item Created an original business idea regarding current technologies.
\item Business plan developed in a team.
\item Pitch made to business owners.
\end{itemize}


\section{Volunteering} 
               {\bf Science Mentor,} Ladybridge High School, Bolton    \hfill       2011--2012
                \begin{itemize} \itemsep -2pt
              \item Mentored pre-GCSE students struggling in the Sciences.
         		\end{itemize}
		{\bf Mathematics Mentor,} Bolton School Boys' Division \hfill 2011--2012
                \begin{itemize} \itemsep -2pt
                 \item  Mentored students who have difficulties with Maths.
		 \end{itemize}
                  {\bf  Young Leader,} Bolton Lads and Girls Club    \hfill   Spring 2012
                 \begin{itemize} \itemsep -2pt
               \item    Supervised children and helped organise activities.
		\end{itemize}
	{\bf Vfifty award}
	\begin{itemize}
	\item Over 50 hours of volunteering in one Academic year 
		 \end{itemize}

\section{Achievements} 
\begin{itemize}\itemsep -2pt
\item EPSRC bursary award for Undergraduate Research Opportunities Programme
\item Gold Crest Award for completion of Engineering Education Scheme.
\item Mathematics Prize for best in A-levels
\item Duke of Edinburgh Silver: Sea Kayaking expedition with team of 4  
%Vfifty award for over 50 hours volunteering in one Academic year \\
%Business Enterprise and Training Course: Created a business idea, developed in groups and made a pitch to business owners.\\
\item Trinity Guildhall Classical Guitar Grades: 1, 2, 5 and 7
\item Vipassana 10-Day Meditation Course completion

 \end{itemize}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\singlespacing
%\newpage
\section{Skills}
   {\bf Programming Languages:} 
 Python, AVR Assembler.\\
  %  \underline{Programming Languages:} & Python \\
     {\bf Software:} 
 Origin, \LaTeX, LTSpice, Microsoft Office, Ableton.\\
{\bf Languages:}
 Japanese (Level 1), Russian (GCSE)
\singlespacing

\section{Interests}
\begin{itemize}\itemsep -2pt
\item Weightlifting: Attend the gym 4 times a week
\item Climbing: Member of Imperial College Mountaineering Club
\item Music Production: Member of Imperial College Music Technology
\item Philosophy: Member of Imperial College Socratic Society
%Classical Guitar\\
\item Meditation
%Tennis
\end{itemize}
\section{References}
Available on request

\end{resume} 
\end{document} 



