
% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[12pt, margin]{res} 
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.5in}
\addtolength{\oddsidemargin}{-0.5in}

% the margin option causes section titles to appear to the left of body text 
\textwidth=5.9in % increase textwidth to get smaller right margin
%\usepackage[cmintegrals,cmbraces]{newtxmath}
%\%usepackage{ebgaramond-maths}
%\usepackage[T1]{fontenc}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage{utopia}
%
%\usepackage{literat}
%\usepackage[urw-garamond]{mathdesign}
%\usepackage[T1]{fontenc}
\usepackage{setspace}
\renewcommand{\baselinestretch}{0.5} 
%\renewcommand{\familydefault}{\sfdefault}
%\renewcommand*\rmdefault{ppl}
%\renewcommand*\rmdefault{iwona}

\begin{document} 

\name{Tigany Noor Abubaker Tigany Zarrouk\\ Email: tiganyzarrouk@gmail.com\\ Tel: +447833198259\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Present Address} \\ 119 Latymer Court \\ Hammersmith Road \\ London, W6 7JF}
\address{{\bf Permanent Address} \\ 174 Crompton Way \\ Bolton, BL2 2SA \\}

 
\begin{resume} 
 
%\section{Objective} 
%Auditing/Analysis of Operations 

\section{Education}
{\bf Imperial College London}\hfill September 2013--June 2017\\
MSci. Hons. Physics (Expected 2:1)---4\textsuperscript{th} Year Undergraduate\\
%Relevant courses
Computational Physics, Physics of the Universe, Cosmology, Light and Matter,  Group Theory, General Relativity, Quantum Field Theory, Advanced Classical Mechanics, Nuclear and Particle Physics, Mathematical Methods.

{\bf Bolton School Boys' Division} \hfill 2006--2013 \\
A-levels: Physics (A*), Maths (A*), Further Maths (A*), Chemistry (A)\\
GCSE's: 6 A*s, 4 As
 

\section{Relevant\\ Experience}

%\singlespacing
 {\bf Undergraduate Research Opportunities Programme} \hfill July 2016--September 2016 \hfill  Imperial College London
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item 9-week, full-time research placement.
 \item Developed homoepitaxial growth model of GaAs with deposition and diffusion events using a Kinetic Monte Carlo algorithm.
\item Extended model with the addition of another molecular species with differing properties. 
\item Analysed number of adatoms, island size and differences in crystal growth.
\end{itemize}


 {\bf Computational Projects,} Imperial College London \hfill October 2013--Present
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item MSci project:  Developed cellular automaton model of non-linear, electrical wave dynamics in the heart which spontaneously give rise to Atrial Fibrillation. 
\item Modelled silver spheres in resin to find the Critical threshold for conductivity.
\item Optimised the design of a pion accelerator and detector to measure branching ratios.
 \item Investigated the properties and dynamics of solitons under the Kortweg De-Vries Equation.
\item Simulated double pendula and investigated dynamics under varous finite difference methods.



 \end{itemize}


\section{Achievements} 
\begin{itemize}\itemsep -2pt
\item EPSRC bursary award for Undergraduate Research Opportunities Programme
\item Gold Crest Award for completion of Engineering Education Scheme.
\item Mathematics Prize for best in A-levels
%Vfifty award for over 50 hours volunteering in one Academic year \\
%Business Enterprise and Training Course: Created a business idea, developed in groups and made a pitch to business owners.\\
\item Trinity Guildhall Classical Guitar Grades: 1, 2, 5 and 7
\item Vipassana 10-Day Meditation Course completion

 \end{itemize}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\singlespacing
%\newpage
\section{Skills}
   {\bf Programming Languages:} 
 Python, AVR Assembler.\\
  %  \underline{Programming Languages:} & Python \\
     {\bf Software:} 
 Origin, \LaTeX, LTSpice, Microsoft Office, Ableton.\\
{\bf Languages:}
 Japanese (Level 1), Russian (GCSE)
\singlespacing

\section{Interests}
\begin{itemize}\itemsep -2pt
\item Weightlifting: Attend the gym 4 times a week
\item Climbing: Member of Imperial College Mountaineering Club
\item Music Production: Member of Imperial College Music Technology
\item Philosophy: Member of Imperial College Socratic Society
%Classical Guitar\\
\item Meditation
%Tennis
\end{itemize}
\section{References}
Available on request

\end{resume} 
\end{document} 



